Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Our focus lies specifically on the sets $\cross_H(r^*)$ of the rectangles $r^*$ in $R^*_i$, where $\cross_H(r^*)$ --- defined in \eqref{eqn:cross} --- is the set of segments in $H$ crossing $r^*$. The following lemma, proven in Appendix~\ref{app:hv:type1}, presents some useful properties of these sets.

>>>>

Our interest lies specifically in the sets $\cross_H(r^*)$ of the rectangles $r^*$ in $R^*_i$, where $\cross_H(r^*)$ --- defined in \eqref{eqn:cross} --- is the set of segments in $H$ crossing $r^*$. The following lemma, proven in Appendix~\ref{app:hv:type1}, presents some useful properties of these sets.
